---
title: "Community Facts"
subtitle: "For more information, visit aapidata.com/facts/"
output: pdf_document
params:
  Group: NA
  Topics: NA
  dataset: NA
  source: NA
  state_pop: NA
  runst: NA
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \usepackage{fancyhdr}
  - \renewcommand{\familydefault}{\sfdefault}
  - \usepackage{helvet}
  - \renewcommand{\arraystretch}{1.5}

---

\addtolength{\headheight}{3cm}
\pagestyle{fancyplain}
\fancyhf{}
\chead{\includegraphics[height=3cm]{aapidata.png}}
\renewcommand{\headrulewidth}{0pt}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tint)
library(shinythemes)
library(tidyverse)
library(xtable)
library(knitr)
library(kableExtra)
options(tinytex.verbose = TRUE)


# test_dta <- file.path("data", "test_dta.xlsx") 
# dta<- read_excel(test_dta)
# source_dta <- file.path("data", "source_information.xlsx") 
# source<- read_excel(source_dta)
# 
#  dta<- dta %>% 
#      filter(dta$group %in% params$Group) %>%
#     gather(Estimate, value, -group) 
#   

if("Total Population" %in% params$Topics){
  totpop <-T
}else{
   totpop <-F
}
if("Population Growth" %in% params$Topics){
  popgrowth <-T
}else{
   popgrowth <-F
}
if("Age Distribution" %in% params$Topics){
  age <-T
}else{
   age <-F
}
if("Education" %in% params$Topics){
  edu <- T
}else{
   edu <-F
}
if("Income and Poverty" %in% params$Topics){
  incomepov<-T
}else{
   incomepov <-F
}
if("Political Participation" %in% params$Topics){
  political <- T
}else{
   political <-F
}
if("Language" %in% params$Topics){
  language<-T
}else{
   language <-F
}
if("Nativity" %in% params$Topics){
  nativity <- T
}else{
   nativity <-F
}
if("Health Insurance" %in% params$Topics){
  healthins<-T
}else{
   healthins <-F
}
if("Homeownership" %in% params$Topics){
  homeownership<-T
}else{
   homeownership <-F
}    

```



## Your Fact Sheet for: `r params$Group`



`r if(totpop == T)'## Total Population'`


```{r totalpop, echo=FALSE, message=FALSE, warning=FALSE, eval= totpop == T}

dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Total Population") %>% pull(output) %>% data.frame()%>% rename(` `= label)


kable(dta_showme,format = "latex",align=c("l","c","c","c")) %>%
  kable_styling( full_width = T,font_size=11) %>%
  row_spec(0, bold=T)%>%
   column_spec(1, width = "90em") 
```


`r if(popgrowth == T)'## Population Growth'`


```{r popgrowth, echo=FALSE, message=FALSE, warning=FALSE, eval= popgrowth == T}
 # dta<- dta %>%  mutate(value = case_when(
 #    Estimate == "Median Income" ~ scales::dollar(value),
 #    Estimate == "Total Population" ~ scales::comma(value),
 #    Estimate == "BA or Higher" ~ paste(value*100,"%",sep = ""),
 #    Estimate == "Percent No Health Insurance" ~ paste(value*100,"%",sep = ""))) %>%
 #    spread(group, value) %>% filter(Estimate %in% params$Topics) 

dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Population Growth") %>% pull(output) %>% data.frame()%>% rename(` `= label)

kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling( full_width = T,font_size=11) %>%
  row_spec(0, bold=T) %>%
   column_spec(1, width = "90em")

```

`r if(age == T)'## Age Distribution'`


```{r age, echo=FALSE, message=FALSE, warning=FALSE, eval= age== T}

dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Age Distribution") %>% pull(output) %>% data.frame()%>% rename(` `= label)

kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling( full_width = T,font_size=11) %>%
  row_spec(0, bold=T) %>%
   column_spec(1, width = "90em")

```



`r if(params$runst==T)'## Top States'`

```{r state_pop, echo=FALSE, message=FALSE, warning=FALSE , eval= params$runst == T}
 # dta<- dta %>%  mutate(value = case_when(
 #    Estimate == "Median Income" ~ scales::dollar(value),
 #    Estimate == "Total Population" ~ scales::comma(value),
 #    Estimate == "BA or Higher" ~ paste(value*100,"%",sep = ""),
 #    Estimate == "Percent No Health Insurance" ~ paste(value*100,"%",sep = ""))) %>%
 #    spread(group, value) %>% filter(Estimate %in% params$Topics) 

kable(params$state_pop,format = "latex", align=c("l","c","c","c")) %>% 
  kable_styling(full_width = T,font_size=11)%>%
  row_spec(0, bold=T) %>%
   column_spec(1, width = "90em")

```



`r if(edu == T)'## Education'`

```{r education, echo=FALSE, message=FALSE, warning=FALSE, eval= edu == T}
dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Education") %>% pull(output) %>% data.frame()%>% rename(` `= label)

kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling(  full_width = T,font_size=11)%>%
  row_spec(0, bold=T) %>%
  column_spec(1, width = "30em")

```

`r if(incomepov == T)'## Income and Poverty'`


```{r income_pov, echo=FALSE, message=FALSE, warning=FALSE, eval= incomepov == T}
dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Income and Poverty") %>% pull(output) %>% data.frame()%>% rename(` `= label)


kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling(full_width = T,font_size=11)%>%
  row_spec(0, bold=T) %>%
   column_spec(1, width = "90em")

```


`r if(political == T)'## Political Participation'`

```{r political, echo=FALSE, message=FALSE, warning=FALSE, eval= political == T}
dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Political Participation") %>% pull(output) %>% data.frame()%>% rename(` `= label)

kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling( full_width = T,font_size=11)%>%
  row_spec(0, bold=T)%>%
   column_spec(1, width = "90em")

```

`r if(language == T)'## Language'`


```{r language, echo=FALSE, message=FALSE, warning=FALSE, eval= language == T}
dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Language") %>% pull(output) %>% data.frame()%>% rename(` `= label)


kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling( full_width = T,font_size=11)%>%
  row_spec(0, bold=T) %>%
   column_spec(1, width = "90em")

```


`r if(nativity == T)'## Nativity'`


```{r nativity, echo=FALSE, message=FALSE, warning=FALSE, eval= nativity == T}
dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Nativity") %>% pull(output) %>% data.frame()%>% rename(` `= label)


kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling(full_width = T,font_size=11)%>%
  row_spec(0, bold=T)%>%
   column_spec(1, width = "90em")

```

`r if(healthins == T)'## Health Insurance'`


```{r healthins, echo=FALSE, message=FALSE, warning=FALSE, eval= healthins == T}
dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Health Insurance") %>% pull(output) %>% data.frame()%>% rename(` `= label)


kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling(full_width = T,font_size=11)%>%
  row_spec(0, bold=T)%>%
   column_spec(1, width = "90em")

```


`r if(homeownership == T)'## Homeownership'`


```{r homeownership, echo=FALSE, message=FALSE, warning=FALSE, eval= homeownership == T}
dta_showme <- 
      params$dataset %>% 
        filter(topic_group == "Homeownership") %>% pull(output) %>% data.frame()%>% rename(` `= label)


kable(dta_showme,format = "latex", align=c("l","c","c","c")) %>%
  kable_styling(full_width = T,font_size=11)%>%
  row_spec(0, bold=T) %>%
   column_spec(1, width = "90em")

```





\newpage

## Source List


```{r pressure, echo=FALSE, message=FALSE, warning=FALSE}
#source %>% filter(Estimate %in% params$Topics)%>%
  kable(params$source,format = "latex") %>%
  kable_styling(full_width = T) %>%
   column_spec(2, width = "80em")%>% kable_styling(font_size = 10)
```


